Estimating duration in the presence of misclassification

### 2024-07-29 ATACCC.tex
Rob first p75 comment

\begin{algorithm}
\For{$i = 1, \dots, N$}{
  \For{$j = 1, \dots, M$}{
    Sample an individual-level random effects vector $\vec{\phi}_{i,j} \dist \LN(\vec{\mu}_{\phi,g}, \matr{\Sigma}_\phi)$ \;
    Calculate $d_{i,j}$ using \cref{ATACCC:eq:di} \;
  }
  \For{$d = 1, \dots, \dmax$}{
    Set $F_{D,g}^{(i)}(d) = \frac{1}{M} \sum_{j=1}^M \I(d_{i,j} \leq d + 0.5)$ \;
  }
}
  \caption{%
  Algorithm to calculate the Monte Carlo integral in \cref{ATACCC:eq:FDintegral}, producing the posterior distribution of $F_{D,g}(d)$.
  The posterior distribution is represented as a sample $F_{D,g}^{(1)}, \dots, F_{D,g}^{(N)}$.
  $\vec{\mu}_{\phi,g}^{(i)}$ and $\matr{\Sigma}_\phi^{(i)}$ denote the $i$th posterior sample of $\vec{\mu}_{\phi,g}$ and $\matr{\Sigma}_\phi$ respectively, taken from the MCMC output which produced $N$ posterior samples.
  $M$ is the number of individuals to draw, I found $M =\numprint{100000}$ produced stable estimates of the tail of $F_{D,g}(d)$ if $\dmax = 45$.
 }
 \label{ATACCC:alg:MonteCarlo}
\end{algorithm}

>>>>

\begin{algorithm}
\For{$i = 1, \dots, N$}{
  \For{$j = 1, \dots, M$}{
    Sample an individual-level random effects vector $\vec{\phi}_{i,j} \dist \LN(\vec{\mu}_{\phi,g}^{(i)}, \matr{\Sigma}^{(i)}_\phi)$ \;
    Calculate $d_{i,j}$ using \cref{ATACCC:eq:di} \;
  }
  \For{$d = 1, \dots, \dmax$}{
    Set $F_{D,g}^{(i)}(d) = \frac{1}{M} \sum_{j=1}^M \I(d_{i,j} \leq d + 0.5)$ \;
  }
}
  \caption{%
  Algorithm to calculate the Monte Carlo integral in \cref{ATACCC:eq:FDintegral}, producing the posterior distribution of $F_{D,g}(d)$.
  The posterior distribution is represented as a sample $F_{D,g}^{(1)}, \dots, F_{D,g}^{(N)}$.
  $\vec{\mu}_{\phi,g}^{(i)}$ and $\matr{\Sigma}_\phi^{(i)}$ denote the $i$th posterior sample of $\vec{\mu}_{\phi,g}$ and $\matr{\Sigma}_\phi$ respectively, taken from the MCMC output which produced $N$ posterior samples.
  $M$ is the number of individuals to draw, I found $M =\numprint{100000}$ produced stable estimates of the tail of $F_{D,g}(d)$ if $\dmax = 45$.
 }
 \label{ATACCC:alg:MonteCarlo}
\end{algorithm}
